Clustering: A pipeline to analyse time-course gene expression data

### 2019-02-16 scripts/02_differential_expression_analysis.Rmd
FIX small stuff due to R changing names

@@

pvalues = de_analysis
outname = ".results/pvalues.txt"
write.table(pvalues, outname)
```

>>>>

```{r echo=FALSE}
# Set options
df = 6

# Preprocessing & filtering
is_count = FALSE
take_log = FALSE    
filter_expression = FALSE

# Differential expression analysis
timecourse_contrasts = c("C-K", "C-M")

# Clustering
filter_genes = TRUE
n_genes_to_keep = 5000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

pvalues = de_analysis
outname = ".results/pvalues.txt"
write.table(pvalues, outname, sep="\t")
```

### 2019-02-16 scripts/03_clustering.Rmd
FIX small stuff due to R changing names

# Right now, the package doesn't contain the normalized data
pvalues = read.table(".results/pvalues.txt", sep="\t")
```

@@

# Rescale the centroids
centroids = moanin::rescale_values(kmeans_clusters$centroids, meta)
all_scores = data.frame(row.names=row.names(data))
for(k in 1:n_clusters){
    scores = moanin:::score_genes_centroid(data, centroids[k,])
    all_scores[paste0("cluster_", k)] = scores
}

>>>>

# Right now, the package doesn't contain the normalized data
pvalues = read.table(".results/pvalues.txt", sep="\t", check.names=FALSE)
```

@@

# Rescale the centroids
centroids = moanin:::rescale_values(kmeans_clusters$centroids, meta)
all_scores = data.frame(row.names=row.names(data))
for(k in 1:n_clusters){
    scores = moanin:::score_genes_centroid(data, centroids[k,])
    all_scores[paste0("cluster_", k)] = scores
}
